\documentclass[letterpaper,10.5pt]{article}
% it was 11 earlier i made it 10.5
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}

\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.6in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------

\begin{center}
    \textbf{\Huge \scshape Pritam Majumder} \\ \vspace{1pt}
    \small +91 8777721047 $|$ \href{https://pritammajumder.in}{\underline{Portfolio}} $|$ 
    \href{mailto:mail@pritammajumder.in}{\underline{mail@pritammajumder.in}} $|$ 
    \href{https://www.linkedin.com/in/pritammajumder16}{\underline{LinkedIn}} $|$
    \href{https://github.com/pritammajumder16}{\underline{Github}}   $|$  \href{mailto:mail@pritammajumder.in}{\underline{Email}}
\end{center}


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
\resumeSubheading
      {Full Stack Developer}{March 2024 -- Present}
      {Plutonapps (Whiterose Lab Pvt. Ltd.)}{Kolkata, West Bengal}
      \resumeItemListStart
        \resumeItem{Developed 3 Web apps with \emph{ Next.js, React, Node.js (Express), MongoDB, Mongoose, Tailwind  and Digital Ocean}}
      \resumeItemListEnd
    \resumeSubheading
      {Free Lancing}{Nov 2023 -- Feb 2024}
      {Badshah Sherwani}{Kolkata, West Bengal}
      \resumeItemListStart
        \resumeItem{Developed a web application for a client using MERN stack and Digital Ocean and also did a DSA course}
      \resumeItemListEnd
    \resumeSubheading
      {Team Lead}{March 2021 -- Oct 2023}
      {Blu Cocoon Digital Pvt. Ltd.}{Kolkata, West Bengal}
      \resumeItemListStart
        \resumeItem{Developed and maintained 5 web apps using \emph{ Angular, Node.js, Azure Functions, Azure CosmosDB and MongoDB.}}
        \resumeItem{Managed a team of 20 developers and 4 testers to deliver projects on time and within budget.} \resumeItem{Oversaw project planning, resource allocation, and client communication to ensure client satisfaction.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Javascript, Typescript, C/C++,  HTML/CSS/SCSS} \\
     \textbf{Frameworks}{: React, Angular, Next.js, Node.js, React Native, Tailwind, Azure Functions (NodeJS),  Express, React Three Fiber, Angular Material, Cordova, Node-red, Webrtc} \\\textbf{Database}{: MongoDB/Mongoose, Azure Cosmos DB (Gremlin API), My Sql(Basics)} \\
     \textbf{Developer Tools}{: Git, Docker, Azure cloud platforms, AWS, Digital Ocean} \\
     \textbf{Libraries}{: Passport.js, Mediasoup, Stripe}
    }}
 \end{itemize}
%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Government College of engineering and textile technology}{Berhampore, West bengal}
      {Bachelor of technology, in computer science engineering}{2016 -- 2020}
    \resumeSubheading
      {Kendriya Vidyalaya Command Hospital}{Kolkata, West Bengal}
      {Higher secondary (Science)}{2014 -- 2016}
  \resumeSubHeadingListEnd
%-----------PROJECTS-----------
\section{Personal Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Prit Banking systems} $|$ \emph{Next.js, Tailwind, Mongoose, Plaid, Dwolla, Sentry, Docker}}{\href{https://banking.pritammajumder.in}{\underline{banking.pritammajumder.in}}}
          \resumeItemListStart
            \resumeItem{A web app for users to connect bank accounts, view transactions, manage details, and transfer/request funds.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Prit Meet} $|$ \emph{React, Tailwind, Simple-Peer, Websocket, NodeJS, Express, Docker}}{\href{https://meet.pritammajumder.in}{\underline{meet.pritammajumder.in}}}
          \resumeItemListStart
            \resumeItem{A web app for users to create rooms and communicate through video, audio, text, and screen sharing.}
          \resumeItemListEnd
           \resumeProjectHeading
          {\textbf{Prit Foodie} $|$ \emph{React Native, Tailwind, Mongoose, NodeJS, Express, Typescript, Docker}}{}
          \resumeItemListStart
            \resumeItem{A mobile app to order food online, like swiggy.}
          \resumeItemListEnd
          \resumeProjectHeading
          {\textbf{Prit Closet} $|$ \emph{Angular, SCSS, Mongoose, NodeJS, Express, Docker}}{\href{https://closet.pritammajumder.in}{\underline{closet.pritammajumder.in}}}
          \resumeItemListStart
            \resumeItem{An e-commerce application where admins can upload clothing items, and users can browse and make purchases.}
          \resumeItemListEnd
          \resumeProjectHeading
          {\textbf{Pritam Portfolio} $|$ \emph{React, React Three Fiber, React Three Drei, Tailwind, Docker}}{\href{https://pritammajumder.in}{\underline{pritammajumder.in}}}
          \resumeItemListStart
            \resumeItem{Developed a 3D portfolio to showcase my skills, and let other contact me.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
    \section{Company Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Ekko} $|$ \emph{Next.js, Typescript, Mongoose, Stripe, Digital Ocean}}{Plutonapps Pvt. Ltd.}
          \resumeItemListStart
            \resumeItem{A SaaS platform for plan purchases, custom waitlist CMS, and domain integration, with super admin analytics.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Compareling} $|$ \emph{React, NodeJS, Express, Mongoose, Stripe, Digital Ocean}}{Plutonapps Pvt. Ltd.}
          \resumeItemListStart
            \resumeItem{A service app connecting agencies and users for payment, and developed a super admin side for analytics.} 
          \resumeItemListEnd
           \resumeProjectHeading
          {\textbf{Pitch40} $|$ \emph{React, Node.js, Tailwind, Typescript, Digital Ocean, Websocket}}{Plutonapps Pvt. Ltd.}
          \resumeItemListStart
          \resumeItem{App linking startups \& investors for fundraises \& pitch uploads \& broker facilitation, w/ super admin analytics.}
          \resumeItemListEnd
          \resumeProjectHeading
          {\textbf{i-Create} $|$ \emph{Angular, Azure Functions, scss, NodeJS, Azure CosmosDB, MongoDB, Socket.io}}{Blu Cocoon digital}
          \resumeItemListStart
            \resumeItem{App for Ingredion replacing the iCreate desktop app to fetch government food data and run tests on food items.}
          \resumeItemListEnd   
          \resumeProjectHeading
          {\textbf{i360} $|$ \emph{Angular, Azure Functions, Azure, scss, NodeJS, Azure Cosmos DB, MongoDB}}{Blu Cocoon Digital}
          \resumeItemListStart
            \resumeItem{App for scientists to manage projects, tasks, experiments, tests, \& print barcodes \& gather customer feedback.}
          \resumeItemListEnd
          \resumeProjectHeading
          {\textbf{Document management system} $|$ \emph{Angular, Node-Red, Azure VM, Azure, MongoDB}}{Blu Cocoon Digital}
          \resumeItemListStart
            \resumeItem{An app to centrally manage documents, allowing retrieval through various filters in a directory structure.}
          \resumeItemListEnd
    
       \resumeProjectHeading
  {\textbf{Tapioca Internal and External} $|$ \emph{Angular, Cordova, Azure Functions, MongoDB}}{Blu Cocoon Digital}
  \resumeItemListStart
    \resumeItem{Two apps: 1 for farmers to learn \& manage plantations \& 2nd for Ingredion to manage, buy from, \& help farmers.}
  \resumeItemListEnd
    \resumeSubHeadingListEnd
%-------------------------------------------
\end{document}